Modelling the City of Melbourne Pedestrian Data

### 2017-05-07 presentation/proposal_pres.Rmd
update: added diagram from city of melb. pdf

@@

The City of Melbourne has `r nrow(ped_loc)` sensors installed around Melbourne's CBD  
These sensors are positioned under an awning or street pole, and count the number of people passing each hour

>>>>

---
class: center

@@

The City of Melbourne has `r nrow(ped_loc)` sensors installed around Melbourne's CBD  
- These sensors are positioned under an awning or street pole, and count the number of people passing each hour

![figure of pedestrian sensors](../img/ped_sensors.png)

_source: http://www.pedestrian.melbourne.vic.gov.au/pdf/CityofMelbournePedestrianCountingSystem.pdf _
